---
title: "MY472-AT24-ps1-exercise1"
output: html_document
date: "2024-10-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Loading the package
library(tidyverse)
```

## Data
This file uses the R built-in dataset 'iris'.
```{r load_dataset}
# Load built-in dataset
data("iris")

# Convert to tibble
iris_tibble <- as_tibble(iris)
head(iris_tibble)
```

## Function 1
A function 'calculate_approximate_petal_area()' is defined, which creates a new column in 'iris_tibble' that holds approximate petal area, calculated by multiplying petal length by petal width. The function is called with iris_tibble as the argument. The output shows the modified tibble.
```{r function_1}
# Function to create a new column in the 'iris_tibble' tibble with approximate petal area, calculated by multiplying petal length by petal width.
calculate_approximate_petal_area <- function(data) {
  data <- data %>%
    mutate(Petal.Area = Petal.Length*Petal.Width)
  return(data)
}

# Call calculate_approximate_petal_area on iris_tibble
iris_tibble <- calculate_approximate_petal_area(iris_tibble)
head(iris_tibble)
```

## Function 2
A function 'calculate_approximate_sepal_area()' is defined, which creates a new column in 'iris_tibble' that holds approximate sepal area, calculated by multiplying sepal length by sepal width. The function is called with iris_tibble as the argument. The output shows the modified tibble.
```{r function_1}
# Function to create a new column in the 'iris_tibble' tibble with approximate petal area, calculated by multiplying petal length by petal width.
calculate_approximate_sepal_area <- function(data_new) {
  data_new <- data_new %>%
    mutate(Sepal.Area = Sepal.Length*Sepal.Width)
  return(data_new)
}

# Call calculate_approximate_petal_area on iris_tibble
iris_tibble <- calculate_approximate_sepal_area(iris_tibble)
head(iris_tibble)
```